### 2022-04-14 paper/paper.tex
add missing period at the end of the statment
add latex paper

All major data processing types in \textbf{TSML} are subtypes of the \texttt{Transformer}. There are two major types of transformers, namely: \emph{filters} for data processing and \emph{learners} for machine learning. Both transformers implement the \texttt{fit!} and \texttt{transform!} multi-dispatch functions. All filters are direct subtypes of the \texttt{Transformer} while all learners are subtypes of the \texttt{TSLearner}. The \texttt{TSLearner} is a direct subtype of the \texttt{Transformer}

@@

The \textbf{TSML} workflow borrows the idea of the  \emph{Unix} pipeline\cite{orchestra2014, combineml2016}. 
The \texttt{Pipeline} data type is also a subtype of the \texttt{Transformer} and expects two arguments: input and output. The main elements in a \textbf{TSML} pipeline are series of transformers with each performing one specific task and does it well. The series of filters are used to perform pre-processing of the input while a machine learner at the end of the pipeline is used to learn the \emph{input--output} mapping. From the perspective of using the \texttt{Pipeline} where the last component is a machine learner, the \texttt{fit!} function is the training phase while the \texttt{transform!} function the prediction or classification phase.
\vskip 6pt

>>>>

All major data processing types in \textbf{TSML} are subtypes of the \texttt{Transformer}. There are two major types of transformers, namely: \emph{filters} for data processing and \emph{learners} for machine learning. Both transformers implement the \texttt{fit!} and \texttt{transform!} multi-dispatch functions. All filters are direct subtypes of the \texttt{Transformer} while all learners are subtypes of the \texttt{TSLearner}. The \texttt{TSLearner} is a direct subtype of the \texttt{Transformer}.

@@

The \textbf{TSML} workflow borrows the idea of the  \emph{Unix} pipeline\cite{orchestra2014, combineml2016}. 
The \texttt{Pipeline} data type is also a subtype of the \texttt{Transformer} and expects two arguments: input and output. The main elements in a \textbf{TSML} pipeline are series of transformers with each performing one specific task and does it well. The series of filters are used to perform pre-processing of the input while a machine learner at the end of the pipeline is used to learn the \emph{input--output} mapping. From the perspective of using the \texttt{Pipeline} where the last component is a machine learner, the \texttt{fit!} function is the training phase while the \texttt{transform!} function is the prediction or classification phase.
\vskip 6pt
